---
title: "Question2: Longdon Paged HTML Doc"
author: "20784538"
date: "17 June 2023"
# date: "`r Sys.Date()`"
bibliography: Tex/ref.bib       
output:
  pagedown::html_paged:
    # template: wp_paged.html
    # css: ['wp.css', 'wp-fonts.css', 'wp-page.css']
    css: ["Template/default-fonts-Texevier.css", "Template/default-page-Texevier.css", "Template/default-Texevier.css"]
    csl: Template/harvard-stellenbosch-university.csl # referencing format used.
    template: ["Template/paged-Texevier.html"]

    toc: true
    # change to true for a self-contained document, but it'll be a litte slower for Pandoc to render
    self_contained: TRUE
abstract: |


---

```{r setup, echo = FALSE, message = FALSE, warning = FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.width = 8, fig.height = 6)

options(dplyr.summarise.inform = F)

if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)

list.files('..//..//..//Question1/code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

pacman::p_load(modelsummary, gt, knitr, kableExtra, tidyverse)

# Loading data: 
    weathdat <- read.csv("C:/Users/mishq/OneDrive/Documents/Ro-eagan/Data Science for Econometrics S1/DatsciPractical23/20784538/Question2/data/London/london_weather.csv", header = TRUE)

detailed_weath <- read.csv("C:/Users/mishq/OneDrive/Documents/Ro-eagan/Data Science for Econometrics S1/DatsciPractical23/20784538/Question2/data/London/UKMonthly_Detailed.csv", header = TRUE)

# weathdf <- tibble::tibble(weathdat) %>% mutate(date = as.Date(date, format = "%Y%m%d")) %>% mutate(format(weathdat$date, "%Y"))

```

\newpage

# Introduction {-}

So you want to move to London? Heres why you should maybe think twice, and just consider staying in the place with the best weather (might be bias). 

I will be showing you two graphs and a table to illustrate how little sun London gets, and how much overcast days are basically just a given. Since you like vitamin D so much, why would you then give up Cape Town weather for none of that? 




## What type of days rule the seasons? {-}

To get a picture, here is a graph that shows how much more overcast days there are overall in the year, throughout any given season. Notice that its higher than sunny days? 

```{r seasons,  warning =  FALSE, fig.align = 'center', fig.cap = "Types of days in seasons\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}

# weath_lineplot <- weathdf_quart %>% 
#     group_by(year)
    
sun_plot <- 
    weathdat %>%
    ggplot() +
    geom_line(aes(x = date, y = sunshine, color = seasons), alpha = 0.8, size = 1) +   
    theme_bw() +
    theme(legend.position = "bottom") +
    labs(x = "Year", y = "Quarterly Total Minutes of Sunshine", fill = "Season", title = "Sunny Days in Different Seasons", subtitle = "Minutes of sunshine observed the seasons over the years", caption = "Data: sourced from UK National Weather Service") 
    
cloud_plot <-
weathdat %>% 
    ggplot() +
        geom_line(aes(x = date, y = cloud_cover, color = seasons), alpha = 0.8, size = 1) +   
    theme_bw() +
    theme(legend.position = "bottom") +
    labs(x = "Year", y = "Quarterly Total Minutes of cloud_cover", fill = "Season", title = "Cloudy Days in Different Seasons", subtitle = "Minutes of overcast observed the seasons over the years", caption = "Data: sourced from UK National Weather Service") 

weather_plot <- (sun_plot + cloud_plot) + plot_annotation(title = 'Weather in London over seasons', caption = 'Source: UK National Weather Service') & theme(text = element_text('bold'))

weather_plot

```


<!-- The following is a code chunk. It must have its own unique name (after the r), or no name. After the comma follows commands for R which are self-explanatory. By default, the code and messages will not be printed in your pdf, just the output: 
# This is just a random plot to show you a plot. This is done if the getwd() does not point to your Template's directory.
Set WD below to your project's working directory.-->


#  Methodology \label{Meth} {-}


$$
\beta = \sum_{i = 1}^{\infty}\frac{\alpha^2}{\sigma_{t-1}^2} \\
\int_{x = 1}^{\infty}x_{i} = 1
$$

Writing nice math requires practice. Note I used a forward slashes to make a space in the equations. I can also align equations using  __\&__, and set to numbering only the first line. Now I will have to type ``begin equation'' which is a native \LaTeX command. Here follows a more complicated equation:

## Results {-}

Tables can be included as follows. Use the _xtable_ (or kable) package for tables. Table placement = H implies Latex tries to place the table Here, and not on a new page (there are, however, very many ways to skin this cat. Luckily there are many forums online!).

```{r table-1, echo=TRUE, message=FALSE, warning=FALSE, results="asis"}
library(knitr)
library(kableExtra)

data <- mtcars[1:5,] %>% tibble::as_tibble()

table <- kable(data, row.names = TRUE,
      caption = 'Table with kable() and kablestyling()',
      format = "html", booktabs = T) %>%
        kable_styling(full_width = T,
                      latex_options = c("striped",
                                        "scale_down",
                                        "HOLD_position"),
                      font_size = 13)
table
```


\newpage


# Weather Summary: 

```{r}

library(modelsummary);library(gt)

# modelsummary works well with gt:

Tab <-

datasummary_skim(swiss,
type="numeric",
 histogram=T,
 title = "Summary: Numeric variables", output = "gt") %>%

        # column labels
    tab_spanner(label = 'Statistics', columns = c("Mean", "SD")) %>%
    tab_spanner(label = 'Quantiles', columns = starts_with("P")) %>%
    # footnote
    tab_footnote(footnote = md("A very **important** Footnote."),
                 locations = cells_body(rows = 3, columns = 1)) %>%

    tab_options(data_row.padding = px(4),table.width = pct(60),
            column_labels.font.size = pct(100),
            column_labels.vlines.width = 1, table.font.size = pct(60))

Tab
```




